% !TEX program = xelatex
% !TEX encoding = UTF-8

%---------------------------------------
% Navid Constantinou
%
% URL: http://www.navidconstantinou.com/
%---------------------------------------


\documentclass[10pt, letter]{article}
\usepackage{fontspec}
%\usepackage{academicons}
\usepackage{fontawesome}
\usepackage{fancyhdr,lastpage}
\usepackage{verbatim,placeins}

\usepackage{paralist}
\usepackage{enumerate} %% to check paralist doesn't clash
\usepackage{etaremune}


\def\www{http://www.navidconstantinou.com}

\usepackage{tikz}
\usetikzlibrary{positioning}
\usetikzlibrary{calc}

\usepackage{comment}

% DOCUMENT LAYOUT
\usepackage{geometry}
%\geometry{a4paper, textwidth=5.5in, textheight=9in, marginparsep=7pt, marginparwidth=.6in}
%\geometry{a4paper, top=2cm,bottom=2.5cm,left=2cm,right=2cm,marginparsep=5mm, marginparwidth=15mm,includemp}
\setlength\parindent{0in}

\pagestyle{fancy}
\lhead{CV} \rhead{\today}
\chead{{\large{\bf Navid C. Constantinou}}}

\lhead{} \rhead{}
\chead{}
\fancyhf{} % sets both header and footer to nothing
\renewcommand{\headrulewidth}{0pt}
% your new footer definitions here


\lfoot{} \cfoot{\thepage~/~\pageref*{LastPage}} \rfoot{}



% FONTS
\usepackage{xcolor}
\definecolor{jhublue}{RGB}{0,105,175}
\definecolor{mylightred}{RGB}{211,79,73}
\definecolor{mydarkred}{RGB}{199,44,38}
\definecolor{mylightgreen}{RGB}{78,153,67}
\definecolor{mydarkgreen}{RGB}{43,129,33}
\definecolor{mylightpurple}{RGB}{150,107,178}
\definecolor{mydarkpurple}{RGB}{126,78,160}
\definecolor{mylightblue}{RGB}{49,101,205}
\definecolor{mydarkblue}{RGB}{20,92,205}

\usepackage{xunicode}
\usepackage{xltxtra}
\defaultfontfeatures{Mapping=tex-text}
\setromanfont [Ligatures={Common},Variant=01]{Linux Libertine}
%\setromanfont [Ligatures={Common}, BoldFont={Gentium Basic Bold}, ItalicFont={Gentium Basic Italic}]{Gentium Basic}
\setmonofont[Scale=0.7]{Monaco}
%\setromanfont[Ligatures={Common}, SmallCapsFont={OfficinaSanITC-BookSC}, BoldFont={OfficinaSanITC-MediumOS}, ItalicFont={Officina Serif ITC Book Italic OS}]{Officina Serif ITC Book}
%\setmonofont[Scale=0.7]{Monaco}
\setsansfont [Ligatures={Common}, SmallCapsFont={HoeflerText-Regular}, BoldFont={HoeflerText-Black}, ItalicFont={HoeflerText-Italic}]{Hoefler Text}
% \newfontfamily{\AI}{Academicons.ttf}

% ---- CUSTOM COMMANDS
\newcommand{\amper}{{\fontspec[Scale=.95]{Adobe Caslon Pro}\selectfont\itshape\&}}
%\newcommand{\amper}{{\fontspec[Scale=.95]{Linux Libertine O}\selectfont}}
\newcommand{\html}[1]{\href{#1}{\scriptsize\textsc{[url]}}}
\newcommand{\urllink}[1]{\href{#1}{\scriptsize\textsc{[url]}}}
\newcommand{\pdf}[1]{\href{#1}{\scriptsize\textsc{[pdf]}}}
\renewcommand{\pdf}[1]{\href{#1}{{\fontspec{FontAwesome}{}}}}
\newcommand{\doi}[1]{\href{#1}{\scriptsize\textsc{[doi]}}}
\renewcommand{\doi}[1]{\href{#1}{{\fontspec{Academicons}{}}}}



\newcommand{\arxiv}[1]{\href{#1}{\scriptsize[arXiv]}}
\newcommand{\pji}{\href{http://users.uoa.gr/~pjioannou/}{{\color{black}Petros J. Ioannou}}}
\newcommand{\wryoung}{\href{http://pordlabs.ucsd.edu/wryoung/}{{\color{black}William R. Young}}}
\newcommand{\amhogg}{\href{http://rses.anu.edu.au/people/academics/prof-andy-hogg/}{{\color{black}Andy Hogg}}}
\newcommand{\leventis}{\href{http://www.leventisfoundation.org}{{\color{black}A. G. Leventis Foundation}}}
\newcommand{\onassis}{\href{http://www.onassis.gr}{{\color{black}Alexander S. Onassis Foundation}}}
\newcommand{\ekpa}{National \& Kapodistrian University of Athens}
\newcommand{\UBonn}{\href{http://pi.physik.uni-bonn.de}{{\color{black}Rheinische Friedrich-Wilhelms Universit\"at}}}
\newcommand{\scripps}{
\href{https://scripps.ucsd.edu}{\color{black}Scripps Institution of Oceanography}}
\newcommand{\rses}{
\href{http://rses.anu.edu.au}{\color{black}Research School of Earth Sciences}}
\newcommand{\clex}{
\href{http://climateextremes.org.au}{\color{black}ARC Centre of Excellence for Climate Extremes}}
\newcommand{\anu}{
\href{http://www.anu.edu.au}{\color{black}Australian National University}}
\newcommand{\ucsd}{
\href{http://www.ucsd.edu}{\color{black}University of California San Diego}}

\usepackage[export]{adjustbox}





\tikzset{
  juliadot/.style args={#1,#2}{shape=circle,line width=0.03ex,minimum width=0.4ex,fill=#1,draw=#2}
}

\newcommand\julialetter[1]{{\strut\fontspec{CMU Sans Serif}\bfseries\selectfont{#1}}}

\DeclareRobustCommand\julia{%
\begin{tikzpicture}[baseline=0mm, every node/.style={inner sep=0mm, outer sep=0mm}]
\node[anchor=base]        (j) at (0,0) {\julialetter{\j}};
\node[anchor=base, right=0ex of j] (u) {\julialetter{u}};
\node[anchor=base, right=0ex of u] (l) {\julialetter{l}};
\node[anchor=base, right=0ex of l] (i) {\julialetter{\i}};
\node[anchor=base, right=0ex of i] (a) {\julialetter{a}};
\path let \p1 = (j) in node[juliadot={mylightblue,mydarkblue}] (bluedot) at (\x1+0.02ex,1.4ex) {};
\path let \p1 = (i) in node[juliadot={mylightred,mydarkred}] (reddot) at (\x1,1.4ex) {};
\path let \p1 = (reddot) in node[juliadot={mylightpurple,mydarkpurple}] (purpledot) at (\x1+0.5ex,\y1) {};
\path let \p1 = (reddot) in node[juliadot={mylightgreen,mydarkgreen}] (greendot) at (\x1+0.25ex,\y1+0.42ex) {};
\end{tikzpicture}%
}



%\usepackage{placeins}

\usepackage{marginnote}
\newcommand{\years}[1]{\marginnote{\scriptsize #1}}
\renewcommand*{\raggedleftmarginnote}{}
%\setlength{\marginparsep}{7pt}
\reversemarginpar

\geometry{top=2cm,bottom=2.0cm,left=2.05cm,right=2.05cm, marginparsep=2mm, marginparwidth=15mm,includemp}


% HEADINGS
\usepackage{sectsty}
\usepackage[normalem]{ulem}
\sectionfont{\mdseries\upshape\Large}
\subsectionfont{\mdseries\scshape\normalsize}
\subsubsectionfont{\mdseries\upshape\large}

% PDF SETUP
% ---- FILL IN HERE THE DOC TITLE AND AUTHOR
\usepackage[bookmarks, colorlinks, breaklinks, pdftitle={Navid C. Constantinou - vita},pdfauthor={Navid Constantinou}]{hyperref}
\hypersetup{linkcolor=blue,citecolor=blue,filecolor=black,urlcolor=jhublue}


\begin{document}
\reversemarginpar
{\huge{ \href{http://www.navidconstantinou.com}{\color{jhublue}\bf Navid C. Constantinou}}}\\[.42cm]
\parbox{.57\linewidth}{
{\href{https://rms.arc.gov.au/RMS/Report/Download/Report/1b0c8b2e-7bb0-4f2d-8f52-ad207cfbb41d/219}{\color{black}ARC DECRA Research Fellow}}\\
\rses\\
\anu, Australia\\
\mbox{}\\
%\href{http://wikimediafoundation.org}{wikimediafoundation.org}\\
}
\parbox{.43\linewidth}{
%\textsc{t}\quad\texttt{+30-6972778295} (\textsc{gr})\\
{\fontspec{Arial Unicode MS}{✉}}\hspace{.26cm}\href{mailto:navid.constantinou@anu.edu.au}{navid.constantinou@anu.edu.au}\\
\textsc{w}\hspace{.24cm}\href{\www}{www.navidconstantinou.com}\\
\faGithub\hspace{.24cm}\href{https://github.com/navidcy}{navidcy}\hspace{3.9em}\faVimeo\hspace{.24cm}\href{https://vimeo.com/navidcy}{navidcy}\\
{\fontspec{Academicons}{}}\hspace{.24cm}\href{http://orcid.org/0000-0002-8149-4094}{0000-0002-8149-4094}\\
{\fontspec{Academicons}{}}\hspace{.24cm}\href{https://arxiv.org/a/constantinou_n_1.html}{arXiv/a/constantinou\_n\_1}}






% \renewcommand{\tabcolsep}{0cm}
%
%
% \begin{tabular*}{2in}{l@{\extracolsep{\fill}}c@{\extracolsep{\fill}}l}
% %{Gender}  & : & Male\\
% {Birthdate}  & : & 23 February 1984\\
% {Nationality} & : & Cypriot (\textsc{\href{http://en.wikipedia.org/wiki/Cyprus}{\color{black}cy}})\\%\textbf{Religion} & : & None\\
% %{Family status} & : & Single\\
% \end{tabular*}
%
% \vspace{0.15in}






%\vspace{-2em}\section*{Areas of specialization}%Philosophy of psychology\\[.2cm]
%\begin{itemize}
%\item Atmospheric sciences
%\item Fluid dynamics
%\item Transition to turbulence
%\item Hydrodynamic stability
%\item  Dynamical systems
%\end{itemize}

%\vspace{-2em}\section*{Areas of specialization}%Philosophy of psychology\\[.2cm]
%\begin{itemize}
%\item Atmospheric sciences
%\item Fluid dynamics
%\item Transition to turbulence
%\item Hydrodynamic stability
%\item  Dynamical systems
%\end{itemize}

%
%\subsubsection*{Areas of specialization}%Philosophy of psychology\\[.2cm]
%Atmospheric sciences •  Fluid dynamics • Transition to turbulence • Hydrodynamic stability • Dynamical systems


%\hrule



%{\small \textsc{supervisor:} \pji }\\
%{\small \textsc{thesis:} Formation of large-scale structures by turbulence in rotating planets}\\
%{\small\textsc{research areas:} Atmospheric sciences, fluid dynamics, transition to turbulence, hydrodynamic stability, linear and nonlinear systems}
%
%


%\hrule
\section*{\bf Interests}

\noindent Geophysical fluid dynamics, physical oceanography, atmospheric dynamics, climate, machine learning, fluid mechanics\\[.2cm]


\vspace{-2em}\section*{\bf Education}


\noindent\years{Oct. 2010 -- \\ \mbox{$\;\;\;$}Feb. 2015}\textbf{Ph.D.~in Physics}\\
\emph{\ekpa, Greece}\\
{\small
\begin{tabular*}{\textwidth}{p{2.4cm}c@{\extracolsep{.25cm}}p{12.1cm}}
 \textsc{Supervisor}    & : & \pji\\
\textsc{Thesis} & : & Formation of large-scale structures by turbulence in rotating planets \arxiv{http://arxiv.org/abs/1503.07644} \pdf{\www/theses/PhD_thesis_Navid.pdf}
\end{tabular*}}\\[.2cm]
\years{Sep. 2008 -- \\ \mbox{$\;\;\;$}Jun. 2010}\textbf{M.Sc.~in Physics w/ Honors} {({summa cum laude}, {9.66/10})}\\
Astrophysics, Astronomy and Mechanics\\\emph{\ekpa, Greece}\\[.2cm]
% {\small
% \begin{tabular*}{\textwidth}{p{2.4cm}c@{\extracolsep{.25cm}}p{12.1cm}}
% \textsc{supervisor}    & : & \pji\\
% \textsc{thesis} & : &Transient energy growth in Holmboe instabilities \pdf{\www/theses/MSc_thesis_Navid.pdf}
% \end{tabular*}
% }\\[.2cm]
\years{Sep. 2003 --\\ \mbox{$\;\;\;$}Jun. 2008}\textbf{B.Sc. in Physics w/ Honors} {(summa cum laude, class of 2008 valedictorian, {9.16/10})}\\
\emph{\ekpa, Greece}\\
Exchange through Socrates-Erasmus program during spring semester 2006 at the\\
\emph{\UBonn}, Bonn, Germany\\[.2cm]
\years{Jul. 2001 --\\ \mbox{$\;\;\;$}Aug. 2003}\textbf{Cyprus National Guard}\\Military service (obligatory) as Second Lieutenant in Armored Forces, Cyprus\\[.2cm]
%\years{2001}\textbf{Acropolis Lyceum} {(\emph{19.1/20, Excellent})\\Nicosia, Cyprus

\vspace{-2em}\section*{\bf Experience}

%\noindent\years{Nov. 2020 -- \\ \mbox{$\;\;\;$}}\textbf{Adjunct Visiting Research Scientist}\\
%\emph{\href{https://www.ucy.ac.cy/oceanography/en/}{\color{black}Cyprus Oceanography Center}, \href{https://www.ucy.ac.cy/en/}{\color{black}University of Cyprus}, Cyprus}\\[.2cm]
\noindent\years{June 2021 -- \\ \mbox{$\;\;\;$}}\textbf{\href{https://rms.arc.gov.au/RMS/Report/Download/Report/1b0c8b2e-7bb0-4f2d-8f52-ad207cfbb41d/219}{\color{black}ARC DECRA Research Fellow}}\\
\emph{\href{http://rses.anu.edu.au}{\color{black}Research School of Earth Sciences}, Australian National University, Australia}\\[.2cm]
\noindent\years{May 2018 -- \\ May 2021}\textbf{Research Fellow}, part of the {\href{http://www.climateextremes.org.au}{{\color{black}ARC Centre of Excellence for Climate Extremes}}}\\
\emph{\href{http://rses.anu.edu.au}{\color{black}Research School of Earth Sciences}, Australian National University, Australia} (with \amhogg)\\[.2cm]
\noindent\years{Sep. 2015 -- \\ \mbox{$\;\;\;$}Apr. 2018}\textbf{Postdoctoral Researcher ({\href{https://cpaess.ucar.edu/cgc/class-25}{{\color{black}NOAA Climate \& Global Change Postdoctoral Fellow}}})}\\
\emph{\scripps, University of California San Diego, USA} (with \wryoung)\\[.2cm]
\noindent\years{Jun. 2015 -- \\ \mbox{$\;\;\;$}Aug. 2015}\textbf{Visiting Researcher}\\
\emph{\href{https://www.ucy.ac.cy/oceanography/en/}{\color{black}Cyprus Oceanography Center}, \href{https://www.ucy.ac.cy/en/}{\color{black}University of Cyprus}, Cyprus}\\[.2cm]


\vspace{-2em}\section*{\bf Grants \amper{} Awards}

\noindent\years{2021-2024}\emph{\href{https://rms.arc.gov.au/RMS/Report/Download/Report/1b0c8b2e-7bb0-4f2d-8f52-ad207cfbb41d/219}{\color{black}ARC Discovery Early Researcher Career Award 2021}} (ARC: 300,000$\,$USD + ANU: 100,000$\,$USD)\\[.2cm]
\noindent\years{2019}\emph{Best paper among Early Career Researchers within {\href{http://www.climateextremes.org.au/publications}{{\color{black}ARC Centre of Excellence for Climate Extremes}}}}\\[.2cm]
\years{2015-2017}\emph{\href{http://vsp.ucar.edu/cgc/class-25}{{\color{black}NOAA Climate \& Global Change Postdoctoral Fellowship}}} (150,000$\,$USD)\\[.2cm]
\years{2009-2014}\emph{\onassis}\\Scholarship for the 2\textsuperscript{nd} year of M.Sc. and for 4 years of Ph.D. studies (47,700$\,$USD)\\[.2cm]
\years{2009-2012}\emph{\leventis}\\Scholarship for the 2\textsuperscript{nd} year of M.Sc. and the first 2 years of Ph.D. studies (16,000$\,$USD)
\newpage
\years{2003-2008}\emph{Department of Physics, \ekpa, Greece}\\Valedictorian for class 2008\\1\textsuperscript{st} student for academic years 2003-04 and 2004-05\\
Honorary Scholarship for academic year 2005-06\\[.2cm]
\years{2001}\emph{International Physics Olympiad, June 2001}\\Participation with the national team of Cyprus\\[.2cm]


\vspace{-2em}\section*{\bf Publications}
%\subsubsection*{Submitted$\,$/$\,$In Review}
% Lozano-Dur\'an, A., Nikolaidis, M.-A., \textbf{Constantinou, N. C.}, and Karp, M. Wall turbulence without modal instability of the streaks. (submitted on Oct.~2019, arXiv:\href{https://arxiv.org/abs/1909.05490}{1909.05490}) \pdf{\www/publications/ModallyStableTurb.pdf}\\[.2cm]

%\vspace{-1.5em}

\setdefaultleftmargin{0pt}{}{}{}{}{}

\begin{etaremune}
\item
\textbf{Constantinou, N. C.} and Hogg, A. McC. Intrinsic oceanic decadal variability of upper-ocean heat content. \emph{J.~Climate}. (in press, doi:\href{https://doi.org/10.1175/JCLI-D-20-0962.1}{10.1175/JCLI-D-20-0962.1}) [\href{https://github.com/navidcy/IntrinsicOceanicLFVariabilityUOHC}{datasets and notebooks}] \doi{https://doi.org/10.1175/JCLI-D-20-0962.1} \pdf{\www/publications/intrinsic-oceanic-decadal-variability.pdf}
\item
Martínez-Moreno, J., Hogg, A. McC., England, M. H., \textbf{Constantinou, N. C.}, Kiss, A. E., and Morrison, A. K. Global changes in oceanic mesoscale currents over the satellite altimetry record. \emph{Nat. Clim. Chang.}, \textbf{11}, 397-403. \doi{https://doi.org/10.1038/s41558-021-01006-9} \pdf{\www/publications/global-eke-trends.pdf} (featured in the \href{https://www.climateextremes.org.au/changing-ocean-eddies-reorganise-ocean-energy/}{CLEX} press news; also read about it in \href{https://theconversation.com/satellites-reveal-ocean-currents-are-getting-stronger-with-potentially-significant-implications-for-climate-change-159461}{The Conversation})\\
Selection of Press Coverage: \href{https://www.theguardian.com/environment/2021/apr/23/changes-to-giant-ocean-eddies-could-have-devastating-effects-globally}{The Guardian}, \href{https://www.smh.com.au/environment/climate-change/world-s-oceans-changing-as-currents-show-new-patterns-20210422-p57lcw.html}{The Sydney Monrning Herald}, \href{https://cosmosmagazine.com/earth/oceans/energetic-ocean-eddies-on-the-rise/}{Cosmos Magazine}.
\item
\textbf{Constantinou, N. C.}, Wagner, G. L., Siegelman, L., Pearson, B. C., and Palóczy, A. GeophysicalFlows.jl: Solvers for geophysical fluid dynamics problems in periodic domains on CPUs \& GPUs. \textit{J. Open Source Softw.}, \textbf{6 (60)}, 3053. (\href{https://github.com/FourierFlows/GeophysicalFlows.jl}{code repository}; \href{https://fourierflows.github.io/GeophysicalFlowsDocumentation/stable/}{package documentation}) \doi{https://doi.org/10.21105/joss.03053} \pdf{\www/publications/geophysicalflows.pdf}
\item
Lozano-Dur\'an, A., \textbf{Constantinou, N. C.}, Nikolaidis, M.-A., and Karp, M. (2021). Cause-and-effect of linear mechanisms in wall turbulence. \emph{J. Fluid Mech.}, \textbf{914}, A8.  \doi{https://doi.org/10.1017/jfm.2020.902} \pdf{\www/publications/cause-effect-linearmechanism.pdf}
\item
Lozano-Dur\'an, A., Nikolaidis, M.-A., \textbf{Constantinou, N. C.}, and Karp, M. (2020). Alternative physics to understand wall turbulence: Navier--Stokes equations with modified linear dynamics. \emph{J. Phys.: Conf. Ser.}, \textbf{1522}, 012003. \doi{https://doi.org/10.1088/1742-6596/1522/1/012003} \pdf{\www/publications/multiflow2019-linearmechanism.pdf}
\item
Rocha, C. B., \textbf{Constantinou, N. C.}, Llewellyn Smith, S. G., and Young, W. R. (2020) The Nusselt numbers of horizontal convection. \emph{J. Fluid Mech.}, \textbf{894}, A24. \doi{https://doi.org/10.1017/jfm.2020.269} \pdf{\www/publications/HCNuDefinition.pdf}
\item
\textbf{Constantinou, N. C.} and Hogg, A. McC. (2019). Eddy saturation of the Southern Ocean: a baroclinic versus barotropic perspective. \emph{Geophys. Res. Lett.}, \textbf{46}, 12202–12212. [\href{https://github.com/navidcy/EddySaturation-BtBc-GRL}{datasets and notebooks}] \doi{https://doi.org/10.1029/2019GL084117} \pdf{\www/publications/EddySaturation-BC-BT.pdf}\ (Best Early Career Researcher paper within \href{https://climateextremes.org.au/publications/}{CLEx} for year 2019.)
\item
Martínez-Moreno, J., Hogg, A. McC., Kiss, A. E., \textbf{Constantinou, N. C.}, and Morrison, A. K. (2019). Kinetic energy of eddy-like features from sea surface altimetry. \emph{J. Adv. Model. Earth Sy.}, \textbf{11 (10)}, 3090-3105. \doi{https://doi.org/10.1029/2019MS001769} \pdf{\www/publications/TrackEddies-SSH.pdf}\ (Featured in the \href{https://climateextremes.org.au/research-brief-southern-ocean-vortices-are-changing/}{CLEx} press news.)
\item
Parker, J. B. and \textbf{Constantinou, N. C.} (2019). Magnetic eddy viscosity of mean shear flows in two-dimensional magnetohydrodynamics. \emph{Phys. Rev. Fluids}, \textbf{4}, 083701. \doi{https://doi.org/10.1103/PhysRevFluids.4.083701} \pdf{\www/publications/magneticviscosity-2019.pdf}\ (Featured in the \href{https://www.anu.edu.au/news/all-news/wind-mystery-inside-gas-giant-saturn-begins-to-unravel}{ANU} and \href{https://www.llnl.gov/news/jupiter-shows-its-true-stripes}{LLNL} press news.)
\item
Bakas, N. A., \textbf{Constantinou, N. C.}, and Ioannou, P. J. (2019). Statistical state dynamics of weak jets in barotropic beta-plane turbulence. \emph{J. Atmos. Sci.}, \textbf{76 (3)}, 919-945. \doi{https://doi.org/10.1175/JAS-D-18-0148.1} \pdf{\www/publications/SSD_Eckhaus.pdf}\ (Featured in the \href{https://climateextremes.org.au/research-brief-new-understanding-reveals-how-jets-and-cyclones-interact/}{CLEx} press news.)
\item
\textbf{Constantinou, N. C.} and Parker, J. B. (2018). Magnetic suppression of zonal flows on a beta-plane. \emph{Astrophys.~J.}, \textbf{863}, 46. \doi{https://doi.org/10.3847/1538-4357/aace53} \pdf{\www/publications/magneticZF-2018.pdf}\ (Featured in the \href{http://www.anu.edu.au/news/all-news/study-helps-solve-mystery-under-jupiter%E2%80%99s-coloured-bands}{ANU} and \href{https://www.llnl.gov/news/lab-researchers-find-magnetic-fields-impact-atmospheric-circulation-gas-giant-planets}{LLNL} press news; also read about it in \href{https://theconversation.com/jupiters-magnetic-fields-may-stop-its-wind-bands-from-going-deep-into-the-gas-giant-101324}{The Conversation}.)
\item
\textbf{Constantinou, N. C.} (2018). A barotropic model of eddy saturation. \emph{J. Phys. Oceanogr.}, \textbf{48(2)}, 397-411. \doi{http://dx.doi.org/10.1175/JPO-D-17-0182.1} \pdf{\www/publications/EddySaturation-JPO-2018.pdf}
\item
\textbf{Constantinou, N. C.} and Young, W. R. (2017). Beta-plane turbulence above monoscale topography. \emph{J. Fluid Mech.}, \textbf{827}, 415-447. \doi{10.1017/jfm.2017.482} \pdf{\www/publications/betaplane-topo-1.pdf}
\item
Farrell, B. F., Ioannou, P. J., Jim\'enez, J., \textbf{Constantinou, N. C.}, Lozano-Dur\'an, A., and Nikolaidis, M.-A. (2016). A statistical state dynamics-based study of the structure and mechanism of large-scale motions in plane Poiseuille flow. \emph{J. Fluid Mech.}, \textbf{809}, 290-315. \doi{http://dx.doi.org/10.1017/jfm.2016.661} \pdf{\www/publications/VLSM-Poiseuille.pdf}
\item
\textbf{Constantinou, N. C.}, Farrell, B. F., and Ioannou, P. J. (2016). Statistical state dynamics of jet--wave coexistence in barotropic beta-plane turbulence. \emph{J. Atmos. Sci.}, \textbf{73 (5)}, 2229-2253.  \doi{http://dx.doi.org/10.1175/JAS-D-15-0288.1} \pdf{\www/publications/SSD_JetWave.pdf} 
\item
Bakas, N. A., \textbf{Constantinou, N. C.}, and Ioannou, P. J. (2015). S3T stability of the homogeneous  state of barotropic beta-plane turbulence. \emph{J. Atmos. Sci.}, \textbf{72 (5)}, 1689-1712. \doi{http://dx.doi.org/10.1175/JAS-D-14-0213.1} \pdf{\www/publications/S3T_barotropic_stability.pdf} 
\item
\textbf{Constantinou, N. C.}, Lozano-Dur\'an, A., Nikolaidis, M.-A., Farrell, B. F., Ioannou, P. J., and Jim\'enez, J. (2014). Turbulence in the highly restricted dynamics of a closure at second order: comparison with DNS. \emph{J. Phys.: Conf. Ser.}, \textbf{506}, 012004. \doi{http://dx.doi.org/10.1088/1742-6596/506/1/012004} \pdf{http://iopscience.iop.org/1742-6596/506/1/012004/pdf/1742-6596_506_1_012004.pdf}
\item
\textbf{Constantinou, N. C.}, Farrell, B. F., and Ioannou, P. J. (2014). Emergence and equilibration of jets in beta-plane turbulence: applications of Stochastic Structural Stability Theory. \emph{J. Atmos. Sci.}, \textbf{71 (5)}, 1818-1842.~\doi{http://dx.doi.org/10.1175/JAS-D-13-076.1} \pdf{\www/publications/S3T_jas.pdf}
\item
\textbf{Constantinou, N. C.} and Ioannou, P. J. (2011). Optimal excitation of two dimensional Holmboe instabilities. \emph{Phys. Fluids}, \textbf{23}, 074102. \doi{http://dx.doi.org/10.1063/1.3609283} \pdf{\www/publications/holmboe.pdf}
\end{etaremune}

\vspace{-1.5em}


\subsubsection*{Chapters in Books (refereed)}
\begin{etaremune}
\item
\textbf{Constantinou, N. C.}, Ioannou, P. J., and Bakas, N. A. (2016). Structure and stability of low amplitude jet equilibria in barotropic turbulence. In Karacostas, T., Bais, A., and Nastos, T. P. (eds.) \textit{Perspectives on Atmospheric Sciences}, 369-375, Springer International Publishing. \doi{http://dx.doi.org/10.1007/978-3-319-35095-0_52} \pdf{\www/publications/S3T_eckhaus-comecap-2016.pdf}
\item
Bakas, N. A., \textbf{Constantinou, N. C.}, and Ioannou, P. J. (2016). On the dynamics underlying the emergence of coherent structures in barotropic turbulence. In Karacostas, T., Bais, A., and Nastos, T. P. (eds.) \textit{Perspectives on Atmospheric Sciences}, 361-367, Springer International Publishing. \doi{http://dx.doi.org/10.1007/978-3-319-35095-0_51} \pdf{\www/publications/S3T_stab-comecap-2016.pdf}
\end{etaremune}

\vspace{-1.5em}

\subsubsection*{Conference Proceedings (refereed)}
\begin{etaremune}
%%{Constantinou, N. C.}, N. A. Bakas and P. J. Ioannou: Equilibration of the jet forming instability in barotropic beta-plane turbulence,  \textit{Geophysical Research Abstracts}, \textbf{18}, EGU2016\mbox{-}2152, 2016.\\[.2cm]
%%Bakas, N. A., {N. C. Constantinou} and P. J. Ioannou: On the dynamics underlying the emergence of large scale structures in barotropic beta-plane turbulence,  \textit{Geophysical Research Abstracts}, \textbf{18}, EGU2016\mbox{-}2143, 2016.\\[.2cm]
%%{Constantinou, N. C.}, B. F. Farrell and P. J. Ioannou: Statistical state dynamics of jet--wave coexistence in beta-plane turbulence. \textit{APS March Meeting 2016}, Baltimore, 14-18 Mar., 2016 \\[.2cm] %\pdf{\www/simplified_RNL_ROI2014.pdf}\\[.2cm]
\item
Ioannou, P. J., Nikolaidis, M.-A., and \textbf{Constantinou, N. C.} (2014) Simplified turbulence in wall-bounded flows. \textit{9th Panhellenic Meeting ``Fluid Flow Phenomena'' (ROH 2014)}, Athens, 12-13 Dec., 2014 (in greek).  \pdf{\www/publications/simplified_RNL_ROI2014.pdf}
%%Loz\'ano-Duran, A., J. Jim\'enez, B. F. Farrell, P. J. Ioannou, M.-A. Nikolaidis and N. C. Constantinou: A restricted nonlinear-dynamics model for turbulent channel flows. \textit{Bulletin of the APS}, 67th Annual Meeting of the APS, DFD, November 23-25, 2014, San Francisco, California, \textbf{59~(20)}, 2014. \html{http://meetings.aps.org/Meeting/DFD14/Session/H25.5} \pdf{http://absimage.aps.org/image/DFD14/MWS_DFD14-2014-000485.pdf}\\[.2cm]
\item
Bakas, N. A., Ioannou P. J., and \textbf{Constantinou, N. C.} (2014). Emergence of non-zonal coherent structures in barotropic turbulence. In  Kanakidou, M., Mihalopoulos, N. and Nastos, P. (eds.) \textit{Proceedings of the 12th International Conference on Meteorology, Climatology \& Atmospheric Physics (COMECAP)}, Heraklion, Crete, 28-31 May, Vol.~1, 107-111, ISBN: 978-960-524-430-9.~\pdf{\www/publications/bakas-etal-comecap-2014.pdf}
\item
\textbf{Constantinou, N. C.} and Ioannou, P. J. (2014). Emergence and equilibration of zonal winds in turbulent planetary atmospheres.  In  Kanakidou, M., Mihalopoulos, N. and Nastos, P. (eds.) \textit{Proceedings of the 12th International Conference on Meteorology, Climatology \& Atmospheric Physics (COMECAP)}, Heraklion, Crete, 28-31 May, Vol.~1, 210-214, ISBN: 978-960-524-430-9.~\pdf{\www/publications/constantinou-ioannou-comecap-2014.pdf}
%%Farrell, B. F.,  P. J. Ioannou and {N. C. Constantinou}: Using statistical mean state dynamics to understand jet and zonon formation in beta-plane turbulence, \textit{AGU Fall Meeting}, NG23A-1489, 2013. \html{http://abstractsearch.agu.org/meetings/2013/FM/sections/NG/sessions/NG23A/abstracts/NG23A-1489.html}\\[.2cm]
%%{Constantinou, N. C.} and P. J. Ioannou: Emergence and equilibration of jets in planetary turbulence,  \textit{Geophysical Research Abstracts}, \textbf{15}, EGU2013\mbox{-}718-1, 2013. \pdf{http://pordlabs.ucsd.edu/navid/EGU2013-718-1.pdf}\\[.2cm]
%%Farrell, B. F., {N. C. Constantinou} and P. J. Ioannou: Testing Stochastic Structural Stability Theory predictions for turbulent jet formation and equilibration in barotropic beta-plane turbulence using nonlinear and quasi-linear simulations, \textit{AGU Fall Meeting}, NG23A-1554, 2012. \html{http://fallmeeting.agu.org/2012/eposters/eposter/ng23a-1554/}\\[.2cm]
%%Bakas, N. A., P. J. Ioannou and {N. C. Constantinou}: Stochastic structural stability theory of the Antarctic Circumpolar Current, \textit{Geophysical Research Abstracts}, \textbf{14}, EGU2012\mbox{-}5769, 2012. \pdf{http://pordlabs.ucsd.edu/EGU2012-5769.pdf}\\[.2cm]
\end{etaremune}

\vspace{-1.5em}

\subsubsection*{Other publications}
\begin{etaremune}
\item
\textbf{Constantinou, N. C.}, Martínez-Moreno, J., Hogg, A. McC., England, M. H., Kiss, A. E., and Morrison, A. K. (2021). Satellites reveal ocean currents are getting stronger, with potentially significant implications for climate change. \textit{The Conversation}, 23rd April 2021. \urllink
{https://theconversation.com/satellites-reveal-ocean-currents-are-getting-stronger-with-potentially-significant-implications-for-climate-change-159461}
\item
Lozano-Dur\'an, A., Nikolaidis, M.-A., \textbf{Constantinou, N. C.}, and Karp, M. Wall turbulence without modal instability of the streaks. (arXiv:\href{https://arxiv.org/abs/1909.05490}{1909.05490}) \pdf{\www/publications/ModallyStableTurb.pdf}
\item
Lozano-Dur\'an, A., Karp, M., and \textbf{Constantinou, N. C.} (2018). Wall turbulence with constrained energy extraction from the mean flow. \textit{Center for Turbulence Research – Annual Research Briefs 2018}, 209-220. \pdf{\www/publications/WallTurbulenceEnergyExtraction.pdf}
\item
\textbf{Constantinou, N. C.} (2018). Jupiter's magnetic fields may stop its wind bands from going deep into the gas giant. \textit{The Conversation}, 10th August 2018. \urllink
{https://theconversation.com/jupiters-magnetic-fields-may-stop-its-wind-bands-from-going-deep-into-the-gas-giant-101324}
\end{etaremune}

\vspace{-2em}\section*{\bf Conferences}
Cause-and-effect of linear mechanisms in wall turbulence. \textit{73rd APS Division of Fluid Dynamics Meeting}, Chicago, IL, USA, 22-24~Nov.~2020. (virtual talk) \pdf{\www/presentations/APS-DFD-2020.pdf} \href{https://youtu.be/tDV6j9WjhIY}{\scriptsize\textsc{[video]}}\\[.2cm]
Eddy saturation of the Southern Ocean: a baroclinic versus barotropic perspective. \textit{Ocean Sciences Meeting 2020}, San Diego, CA, USA, 16-21~Feb.~2020. (poster) \pdf{\www/presentations/OSM_Feb2020-poster.pdf}\\[.2cm]
Demystifying the Southern Ocean's response to wind variability. \textit{ARC Centre of Excellence for Climate Extremes Annual Workshop 2019} \urllink{https://climateextremes.org.au/arc-centre-of-excellence-for-climate-extremes-workshop-2019-hobart/}, Hobart, Tasmania, Australia, 19-21~Nov.~2019. (\textbf{invited talk}) \pdf{\www/presentations/CLEX-SouthernOcean_Nov2019.pdf}\\[.2cm]
Barotropic versus baroclinic eddy saturation: implications to Southern Ocean dynamics. \textit{22nd Conference on Atmospheric and Oceanic Fluid Dynamics}, Portland ME, USA, 24-28~Jun.~2019. (talk) \pdf{\www/presentations/AOFD_Jun2019.pdf}\\[.2cm]
Magnetic eddy viscosity of mean shear flows in 2D magnetohydrodynamics: possible application to gas giants' interiors. \textit{22nd Conference on Atmospheric and Oceanic Fluid Dynamics}, Portland ME, USA, 24-28~Jun.~2019. (poster) \pdf{\www/presentations/AOFD_Jun2019-poster.pdf}\\[.2cm]
Barotropic versus baroclinic eddy saturation. \textit{AGU Fall Meeting 2018}, Washington DC, USA, 10-14~Dec.~2018. (poster) \pdf{\www/presentations/AGU2018_ocean-poster.pdf}\\[.2cm]
Magnetic suppression of zonal flows on a beta plane. \textit{AGU Fall Meeting 2018}, Washington DC, USA, 10-14~Dec.~2018. (poster) \pdf{\www/presentations/AGU2018_magnetic-poster.pdf}\\[.2cm]
Statistical state dynamics reveals mechanism for organization of coherent structures in turbulent flows. \textit{Euromech Colloquium 598: Coherent structures in wall-bounded turbulence}, Imperial College London, London, UK, 29-31~Aug.~2018. (\textbf{invited keynote talk}) \pdf{\www/presentations/Euromech598_Aug2018.pdf}\\[.2cm]
Eddy saturation in a barotropic model. \textit{21st Conference on Atmospheric and Oceanic Fluid Dynamics}, Portland OR, USA, 25-30~Jun.~2017. (talk) \pdf{\www/presentations/AOFD_Jun2017.pdf}\\[.2cm]
A statistical state dynamics based theory for jet--wave coexistence in beta-plane turbulence. \textit{21st Conference on Atmospheric and Oceanic Fluid Dynamics}, Portland OR, USA, 25-30~Jun.~2017. (poster) \pdf{\www/presentations/AOFD_Jun2017-poster.pdf}\\[.2cm]
Understanding self-organization in turbulent flows by studying the statistical state dynamics, \textit{Conference on ``Recurrence, self-organization, and the dynamics of turbulence''}, KITP, UC Santa Barbara, USA, 9-13~Jan.~2017. (\textbf{invited talk}) \pdf{\www/presentations/KITP_Jan2017.pdf}\\[.2cm]
Topographic beta-plane turbulence and form stress. \textit{AGU Fall Meeting 2016}, San Francisco, USA, 12-16~Dec.~2016. (poster) \pdf{\www/presentations/AGU2016_poster.pdf}\\[.2cm]
Structure and mechanism of turbulence under dynamical restriction in plane Poiseuille flow. \textit{69th APS Division of Fluid Dynamics Meeting}, Portland, USA, 20-22~Nov.~2016. (talk) \pdf{\www/presentations/APS-DFD-2016.pdf} \\[.2cm]
Statistical state dynamics of jet--wave coexistence in beta-plane turbulence. \textit{APS March Meeting 2016}, Baltimore, USA, 14-18 Mar., 2016. (talk) \pdf{\www/presentations/APS_Mar2016.pdf} \\[.2cm]
Emergence and equilibration of zonal winds in turbulent planetary atmospheres. \textit{12th International Conference on Meteorology,
Climatology and Atmospheric Physics, COMECAP 2014} \html{http://comecap2014.chemistry.uoc.gr/}, Heraklion, Crete, Greece, 28-31 May 2014. (poster) \pdf{\www/presentations/COMECAP14_poster.pdf}\\[.2cm]
Emergence and equilibration of jets in planetary turbulence.  \textit{EGU 2013 General Assembly} \html{http://www.egu2013.eu/}, Vienna, Austria, 8-12 Apr. 2013. (talk) \pdf{\www/presentations/EGU13-talk.pdf}
\\[.2cm]
Emergence and equilibration of jets in planetary turbulence.  \textit{8th Panhellenic Meeting ``Fluid Flow Phenomena'' (ROI 2012)} \html{http://www.mie.uth.gr/flow2012/}, Volos, Greece, 16-17 November 2012. (talk) \pdf{\www/presentations/ROI12-talk}\\[.2cm]



\vspace{-2em}\section*{\bf Seminars}

From small swirls up to the global ocean circulation: how ocean eddies affect the Earth’s climate, Research School of Earth Sciences \html{https://earthsciences.anu.edu.au/}, Australian National University, Canberra, Australia, 25 Mar. 2021. (\textbf{invited talk}) \href{\www/presentations/RSES-EddiesClimate_Mar2021.pdf}{{\fontspec{FontAwesome}{}}} \href{https://www.youtube.com/watch?v=PPz8bD-vJmI&list=PLyZME1ti5Gk3RzPpheCQmtA7XUlqNT7LY&index=25}{\scriptsize\textsc{[video]}}\\[.2cm]
Cause-and-effect of linear mechanisms in wall turbulence. Shear Flow Instability, Transition and Turbulence Seminar Series, Monash University \html{https://www.monash.edu}, (via Zoom), 7 Oct. 2020.  \href{\www/presentations/Monash-ShearTurbulence-Oct2020.pdf}{{\fontspec{FontAwesome}{}}}\\[.2cm]
What's underneath Jupiter's and Saturn's stripes? FEARS Meeting, Research School of Astronomy and Astrophysics \html{http://rsaa.anu.edu.au/}, Australian National University, Canberra, Australia, 29 Oct. 2019. \href{\www/presentations/RSAA-MagneticViscosity_Oct2019.pdf}{{\fontspec{FontAwesome}{}}}\\[.2cm]
What is hiding underneath the stripes of Jupiter and Saturn? Department of Physics Colloquium, Department of Physics \html{http://en.phys.uoa.gr/}, National and Kapodistrian University of Athens \html{http://en.uoa.gr/}, Athens, Greece, 16 Oct. 2019. \href{\www/presentations/UoA-MagneticViscosity_Oct2019.pdf}{{\fontspec{FontAwesome}{}}}\\[.2cm]
Barotropic versus baroclinic eddy saturation: implications to Southern Ocean dynamics. Geophysical Fluid Dynamics Summer Program, Woods Hole Oceanographic Institution \html{https://www.whoi.edu/gfd}, Woods Hole, USA, 9 Jul. 2019. \href{\www/presentations/EddySaturation-GFD-2019.pdf}{{\fontspec{FontAwesome}{}}}\\[.2cm]
Barotropic versus baroclinic eddy saturation: implications to Southern Ocean dynamics. Geophysical Fluid Dynamics Summer Program, Woods Hole Oceanographic Institution \html{https://www.whoi.edu/gfd}, Woods Hole, USA, 9 Jul. 2019. \href{\www/presentations/EddySaturation-GFD-2019.pdf}{{\fontspec{FontAwesome}{}}}\\[.2cm]
A barotropic process-model for eddy saturation. WHOI Physical Oceanography Seminar Series, Woods Hole Oceanographic Institution \html{https://www.whoi.edu}, Woods Hole, USA, 16 Apr. 2019. \href{http://www.navidconstantinou.com/presentations/WHOI_Apr2019.pdf}{{\fontspec{FontAwesome}{}}}\\[.2cm]
How does the Antarctic Circumpolar Current respond to the increasing winds over the Southern Ocean?
Barotropic versus baroclinic eddy saturation. Physics \& Physical Oceanography Department Seminar Series, University of North Carolina Wilmington \html{https://uncw.edu/phy/}, Wilmington NC, USA, 11 Apr. 2019.\\[.2cm]
How does the Antarctic Circumpolar Current respond to the increasing winds over the Southern Ocean?: Barotropic versus Baroclinic Eddy Saturation. Fluids Seminar Math Department \html{https://www.monash.edu/science/schools/mathematical-sciences}, Monash University \html{https://www.monash.edu}, Melbourne, Australia, 12 Feb. 2019.\\[.2cm]
Statistical state dynamics: a new framework for understanding turbulent flows. Fluid Mechanics Research Group Seminar \html{https://fluids.eng.unimelb.edu.au}, University of Melbourne \html{https://www.unimelb.edu.au}, Melbourne, Australia, 8 Feb. 2019.\\[.2cm]
Magnetic suppression of zonal flows on a beta plane. SpinLab Group Seminar \html{http://spinlab.ess.ucla.edu/}, University of California Los Angeles \html{https://www.ucla.edu}, Los Angeles, CA, USA, 11 Jan. 2019.  \pdf{\www/presentations/GFDL_Dec2018.pdf}\\[.2cm]
Barotropic versus baroclinic eddy saturation. Oceans and Climate Group Seminar \html{https://www.gfdl.noaa.gov/ocean-and-cryosphere-division/}, Geophysical Fluid Dynamics Laboratory \html{https://www.gfdl.noaa.gov/}, Princeton, NJ, USA, 12 Dec. 2018.  \pdf{\www/presentations/GFDL_Dec2018.pdf}\\[.2cm]
Eddy saturation in a barotropic model. LDEO OCP Seminar \html{https://www.ldeo.columbia.edu/research/ocean-climate-physics/seminars}, Lamont-Doherty Earth Observatory \html{https://www.ldeo.columbia.edu}, Columbia University, Palisades, NY, USA, 27 Oct. 2017.  \pdf{\www/presentations/CEAFM_Oct2017.pdf}\\[.2cm]
Eddy saturation in a barotropic model. ClimaTea Seminar \html{https://eps.harvard.edu/eps-event-type/climate-seminar}, Harvard University, Cambridge, MA, USA, 26 Oct. 2017.  \pdf{\www/presentations/CEAFM_Oct2017.pdf}\\[.2cm]
Eddy saturation in a barotropic model. CEAFM Seminar \html{http://pages.jh.edu/~ceafm/}, Department of Earth \& Planetary Sciences, The Johns Hopkins University, Baltimore, USA, 13 Oct. 2017.  \pdf{\www/presentations/CEAFM_Oct2017.pdf}\\[.2cm]
Topographic beta-plane turbulence and form stress. Geophysical Fluid Dynamics Summer Program, Woods Hole Oceanographic Institution \html{https://www.whoi.edu/gfd}, Woods Hole, USA, 19 Jul. 2016. \href{http://www.navidconstantinou.com/presentations/GFD-2016.pdf}{{\fontspec{FontAwesome}{}}}
\\[.2cm]
Topographic beta-plane turbulence and form stress. Mathematics of Turbulence Reunion Conference, IPAM, UCLA \html{http://www.ipam.ucla.edu/}, Lake Arrowhead, 7 Jun. 2016. \href{http://www.navidconstantinou.com/presentations/IPAM_Jun2016.pdf}{{\fontspec{FontAwesome}{}}}
\\[.2cm]
Statistical state dynamics of planetary turbulence. CEAFM Seminar \html{http://pages.jh.edu/~ceafm/}, Whiting School of Engineering, The Johns Hopkins University, Baltimore, 18 Mar. 2016.  \href{http://www.navidconstantinou.com/presentations/CEAFM_Mar2016.pdf}{{\fontspec{FontAwesome}{}}}
\\[.3cm]
A theory for large-scale structure formation in atmospheric/oceanic turbulence: Is jet formation a phase transition phenomenon? CASPO Seminar, Scripps Institution of Oceanography, UC San Diego \html{https://scripps.ucsd.edu/}, La Jolla, 10 Feb. 2016.  \pdf{\www/presentations/CASPO_Feb2016.pdf}
\\[.2cm]
Formation of large-scale structures by turbulence in planetary atmospheres. Physics Department, University of Cyprus \html{https://www.ucy.ac.cy/phy/en/}, Nicosia, 5 May 2015.  \pdf{\www/presentations/UCY_May2015.pdf}
\\[.2cm]
Emergence of large-scale structure in planetary turbulence as an instability of the of the homogeneous turbulent state. IPAM, UCLA \html{http://www.ipam.ucla.edu/}, Los Angeles, 21 Oct. 2014.  \pdf{\www/presentations/IPAM_Oct2014.pdf}
\\[.2cm]
Emergence and equilibration of zonal winds in turbulent planetary atmospheres. Cyprus Oceanography Center, University of Cyprus \html{http://www.oceanography.ucy.ac.cy/}, Nicosia, 7 Jan. 2014.  \pdf{\www/presentations/UCY_Jan2014.pdf}
\\[.2cm]
Verification of the predictions of SSST in nonlinear simulations. 2nd  Meeting of ``Zonal Jets and Eddies'' team, International Space Science Institute (ISSI) \html{http://www.issibern.ch/teams/zonaljets/}, Bern 2-5 Apr. 2013.  \pdf{\www/presentations/ISSI_Apr2013.pdf}\\[.2cm]



%\hrule

\vspace{-2em}\section*{\bf Workshops}

\noindent\years{2021}\textbf{Layering in Atmospheres, Oceans, and Plasmas}\\
Kavli Institute for Theoretical Physics, UC Santa Barbara\\
January 11 - March 12 2021, Santa Barbara (Virtual), CA, USA~\html{https://www.kitp.ucsb.edu/activities/staircase21/}\\[.2cm]
\noindent\years{2019}\textbf{Advanced Ocean Modelling School}\\
University of Tasmania\\
April 28 - May 3, Lake Pedder, Tasmania, Australia~\html{https://climateextremes.org.au/advanced-ocean-modelling-summer-school/}\\[.2cm]
% \noindent\years{2018}\textbf{ARC Centre of Excellence for Climate Extremes Annual Workshop}\\November 19 - November 21, Wollongong, NSW, Australia~\html{https://climateextremes.org.au/event/clex-annual-workshop-2018/}\\[.2cm]
\newpage
\noindent\years{2017}\textbf{Vorticity in the Universe: From Superfluids to Weather and Climate, to the Universe}\\Aspen Center for Physics\\August 27 - September 17 2017, Aspen, CO, USA~\html{http://www.aspenphys.org/}\\[.2cm]
\noindent\years{2017}\textbf{Les Houches Summer School on Fundamental Aspects of Turbulent Flows in Climate Dynamics}\\Les Houches Physics School\\July 31 - August 25 2017, Les Houches, France~\html{https://climate-houches.sciencesconf.org/}\\[.2cm]
\noindent\years{2014}\textbf{Mathematics of Turbulence}\\Institute of Pure \& Applied Mathematics, UCLA\\September 8 - December 12 2014, Los Angeles, USA~\html{https://www.ipam.ucla.edu/programs/long-programs/mathematics-of-turbulence/}\\[.2cm]
\noindent\years{2013}\textbf{Geoturb: Numerical Modeling and Theoretical Challenges in Atmosphere and Ocean Turbulence}\\Ecole normale sup\'erieure de Lyon\\2-4 October 2013, Lyon, France.~\html{http://geoturb.sciencesconf.org/}\\[.2cm]
\noindent\years{2013}\textbf{First Multiflow Summer Workshop}\\Universidad Polit\'ecnica de Madrid\\10 June - 12 July 2013, Madrid, Spain.~\html{https://doi.org/10.1088/1742-6596/506/1/011001}\\[.2cm]
\noindent\years{2011}\textbf{International Graduate School on Stability, Transition to Turbulence and Flow Control}\\Organized by Advanced Instability Methods (AIM) Network\\22-27 August 2011, Cambridge, UK.~\html{http://www2.eng.cam.ac.uk/~mpj1001/AIM_ED.html}\\[.2cm]
\noindent\years{2009}\textbf{Climate Variability \& Climate Change}: \textbf{Estimating and Reducing Uncertainties}\\8-17 June 2009, Visegr\'ad, Hungary.~\html{http://owww.met.hu/omsz.php?almenu_id=omsz&pid=seminars&pri=4&mpx=0}\\[.2cm]




\vspace{-2em}\section*{\bf Teaching Experience}

\noindent\years{Jun.~2021}\textbf{Atmosphere and Ocean Dynamics Winter School 2021}\\
(main lecturer along w/ Martin Singh and Annie Foppert)\\[0pt] 
Australian National University\\[0pt] 
[organized by ARC Centre of Excellence for Climate Extremes; more information \href{https://climateextremes.org.au/winter-school-2021-atmosphere-and-ocean-dynamics/}{online}]\\[.2cm]
\noindent\years{2021}\textbf{Computational Geosciences} (Undergraduate/Honors EMSC4033; Masters EMSC8033)\\
(main lecturer along w/ Louis Moresi)\\[0pt]
[course website at \href{https://github.com/ANU-RSES-Education/EMSC-4033}{github}]\\
Research School of Earth Sciences, Australian National University, Australia\\[.2cm]
\noindent\years{Jun.~2020}\textbf{Atmosphere and Ocean Dynamics Winter School 2020}\\
\textbf{[School Postponed due to COVID-19; 3 introductory lectures were given via Zoom]}\\
(main lecturer along w/ Martin Singh and Annie Foppert)\\[0pt] 
Institute for Marine and Antarctic Studies \& University of Tasmania\\[0pt] 
[organized by ARC Centre of Excellence for Climate Extremes; more information \href{https://climateextremes.org.au/clex-winter-school-2020-atmosphere-and-ocean-dynamics/}{online}]\\[.2cm]
\noindent\years{2020}Course Coordinator for \textbf{Basics of Dynamical Systems and Bifurcation Theory} (Honors/Masters/Graduate)\\[0pt] [3 lectures by Henk Dijkstra; 3 workshops by myself; lecture \& workshop slides/notes available at \href{https://github.com/ClimateFluidPhysics-ANU/DynamicalSystems-BifurcationTheory}{github}]\\
Research School of Earth Sciences, Australian National University, Australia\\[.2cm]
\noindent\years{2018}Course Coordinator for \textbf{Instabilities in Fluids} (Honors/Masters)\\[0pt] [lecture notes and students' project reports available at \href{https://github.com/navidcy/Instabilities-in-Fluids}{github}]\\
Research School of Earth Sciences, Australian National University, Australia\\[.2cm]
\noindent\years{2018}Visiting lecturer for \textbf{Fluid Mechanics} (Undergraduate) [lecture notes available at \href{https://github.com/navidcy/PseudospectralTutorial/tree/master/UNCW2018}{github}]\\
Department of Physics and Physical Oceanography, University of North Carolina Wilmington, USA\\[.2cm]
\noindent\years{2017}Teaching assistant for \textbf{Applied Mathematics III} (Graduate)\\
Scripps Institution of Oceanography, University of California San Diego, USA\\[.2cm]
\noindent\years{2010-2014}Teaching assistant for \textbf{Nonlinear Dynamical Systems} (3rd year Undergraduate)\\
Physics Department, \ekpa, Greece\\[.2cm]

\vspace{-2em}\section*{\bf Student Supervision}
\noindent\years{Oct.~2020 --}Druv Bhagtani (Ph.D. student; co-supervisor).\\[0pt] Project:~``The interplay between wind stress and surface buoyancy in driving large-scale oceanic gyres.''\\[.2cm]
\noindent\years{Jul.~2020 -- \\ \mbox{$\;\;\;$}Nov.~2020}Elise Palethorpe (2rd year undergraduate student).\\[0pt] Project:~``\textbf{Numerical methods for Partial Differential Equations}.''\\[0pt]Aim: Learn basics of finite difference numerical schemes for solving hyperbolic and also study and implement high-order accurate weighted essentially non-oscillatory (WENO) schemes.\\[.2cm]
\noindent\years{Nov.~2019 -- \\ \mbox{$\;\;\;$}Feb.~2020}Fabian Antonio Circelli (3rd year undergraduate student).\\[0pt] Project:~``\textbf{Fourier-based Pseudospectral Methods for Solving Partial Differential Equations}.''\\[0pt]Aim: Learn basics of pseudospectral techniques for solving PDEs and implement GPU functionality in \href{https://github.com/FourierFlows/FourierFlows.jl}{\color{black}FourierFlows.jl} Julia package.\\[.2cm]


\vspace{-2em}\section*{\bf Programming skills}

\href{http://julialang.org}{\color{black}\julia}, \href{https://www.python.org}{\color{black}Python}, Matlab, git, markdown\\[.2cm]

\vspace{-2em}\section*{\bf Open-Source Software}
Core developer for ``\href{https://github.com/FourierFlows/FourierFlows.jl}{\color{black}FourierFlows.jl}'': Julia ecosystem for solving partial differential equations on periodic domains with Fourier-based pseudospectral methods; doi:\href{http://dx.doi.org/10.5281/zenodo.1161724}{\color{jhublue}10.5281/zenodo.1161724}\\[.2cm]
Core developer for ``\href{https://github.com/FourierFlows/GeophysicalFlows.jl}{\color{black}GeophysicalFlows.jl}'': Julia modules for solving problems in Geophysical Fluid Dynamics on periodic domains using Fourier-based pseudospectral methods; doi:\href{http://dx.doi.org/10.5281/zenodo.1161724}{\color{jhublue}10.5281/zenodo.1463809}\\[.2cm]
Contributor for ``\href{https://github.com/CliMA/Oceananigans.jl}{\color{black}Oceananigans.jl}'': A fast and friendly incompressible fluid flow solver in Julia that can be run in 1-3 dimensions on CPUs and GPUs; doi:\href{https://doi.org/10.21105/joss.02018}{\color{jhublue}10.21105/joss.02018}\\[.2cm]
Contributor for ``\href{https://github.com/xgcm/xrft}{\color{black}xrft}'': Python package for taking the discrete Fourier transform (DFT) on xarray and dask arrays; doi:\href{https://doi.org/10.5281/zenodo.1402635}{\color{jhublue}10.5281/zenodo.1402635}\\[.2cm]




\vspace{-2em}\section*{\bf Mobility}

Studied and worked in academic institutions in \textbf{Greece}, \textbf{Cyprus}, \textbf{U.S.A.}, and \textbf{Australia}. Curently, resident of \href{https://en.wikipedia.org/wiki/Broulee,_New_South_Wales}{{\color{black}Broulee, NSW}}.\\[.2cm]


\vspace{-2em}\section*{\bf Other Scientific Activities}

\begin{tabular*}{\textwidth}{p{1.0cm}c@{\extracolsep{.25cm}}p{12.1cm}}
{Reviewer}  & : &  Journal of Fluid Mechanics, Journal of Physical Oceanography, Physics of Plasmas, Physics Letters~A, Scientific Reports, Geophysical Research Letters, Fluids, Journal of Advances in Modeling Earth Systems, Mathematics and Computers in Simulation, Australian Research Council.\\
\end{tabular*}\\[.2cm]




\vspace{-2em}\section*{\bf References}

%\begin{tabular}{p{8cm}p{11cm}}
%\raggedright \textbf{Petros J. Ioannou}\\
%Department of Physics\\
%University of Athens\\
%Zografos, 15784, Greece\\
%{\fontspec{Meiryo}{☎}}\hspace{.188cm}\texttt{\href{skype:+302107276910?sms}{\small +30\;210\;7276910}}\\
%\hspace{.1em}{\fontspec{Arial Unicode MS}{✉}}\hspace{-.1em}\hspace{.32cm}\href{mailto:pjioannou@phys.uoa.gr}{\small pjioannou@phys.uoa.gr}\\
%\hspace{.1em}{w}\hspace{.24cm}\href{http://users.uoa.gr/~pjioannou/}{\small http://users.uoa.gr/$\sim$pjioannou}
%& \small{(Ph.D. thesis advisor)}\\
%\mbox{}&\\
%\raggedright \textbf{Brian F. Farrell}\\
%Department of Earth and Planetary Sciences\\
%Harvard University\\
%Cambridge, MA 02138, USA\\
%{\fontspec{Meiryo}{☎}}\hspace{.188cm}\texttt{\href{skype:+16174952998?sms}{\small +1\;(617)\;495-2998}}\\
%\hspace{.1em}{\fontspec{Arial Unicode MS}{✉}}\hspace{-.1em}\hspace{.32cm}\href{mailto:farrell@seas.harvard.edu}{\small farrell@seas.harvard.edu}\\
%\hspace{.1em}{w}\hspace{.24cm}\href{http://projects.iq.harvard.edu/brian_f_farrell/}{\small http://projects.iq.harvard.edu/brian\_f\_farrell/}
%& \\
%\mbox{}&\\
%\raggedright \textbf{Nikolaos A. Bakas}\\
%Department of Physics\\
%University of Ioannina\\
%Ioannina, 45221, Greece\\
%{\fontspec{Meiryo}{☎}}\hspace{.188cm}\texttt{\href{skype:+302651008599?sms}{\small +30\;26510\;08599}}\\
%\hspace{.1em}{\fontspec{Arial Unicode MS}{✉}}\hspace{-.1em}\hspace{.32cm}\href{mailto:nbakas@uoi.gr}{\small nbakas@uoi.gr}
%&\\
%\mbox{}&\\
%\raggedright \textbf{Theocharis A. Apostolatos}\\
%Department of Physics\\
%University of Athens\\
%Zografos, 15784, Greece\\
%{\fontspec{Meiryo}{☎}}\hspace{.188cm}\texttt{\href{skype:+302107276902?sms}{\small +30\;210\;7276902}}\\
%\hspace{.1em}{\fontspec{Arial Unicode MS}{✉}}\hspace{-.1em}\hspace{.32cm}\href{mailto:thapostol@phys.uoa.gr}{\small thapostol@phys.uoa.gr} \\
%\hspace{.1em}{w}\hspace{.24cm}\href{http://users.uoa.gr/~thapostol/}{\small http://users.uoa.gr/$\sim$thapostol}
%&
%\end{tabular}


\begin{tabular}{p{.5\textwidth}p{.5\textwidth}}
\begin{minipage}[c]{.49\textwidth}
\raggedright \textbf{Petros J. Ioannou} (Ph.D. advisor)\\
Department of Physics\\
\ekpa\\
Zografos, 157\,84, Greece\\
{\fontspec{Meiryo}{☎}}\hspace{.188cm}\texttt{\href{skype:+302107276910?sms}{ +30$\;$210$\;$7276910}}\\
\hspace{.1em}{\fontspec{Arial Unicode MS}{✉}}\hspace{-.1em}\hspace{.32cm}{\small\href{mailto:pjioannou@phys.uoa.gr}{ pjioannou@phys.uoa.gr}}\\
\hspace{.1em}{w}\hspace{.24cm}{\small\href{http://users.uoa.gr/~pjioannou/}{ http://users.uoa.gr/$\sim$pjioannou}}
\end{minipage}%
&
\begin{minipage}[c]{.49\textwidth}
\raggedright \textbf{William R. Young} (postdoc supervisor)\\
Scripps Institution of Oceanography\\
University of California San Diego\\
La Jolla, CA 92037-0213, USA\\
{\fontspec{Meiryo}{☎}}\hspace{.188cm}\texttt{\href{skype:+18585341380?sms}{+1$\;$(858)$\;$534-1380}}\\
\hspace{.1em}{\fontspec{Arial Unicode MS}{✉}}\hspace{-.1em}\hspace{.32cm}{\small\href{mailto:wryoung@ucsd.edu}{wryoung@ucsd.edu}}\\
\hspace{.1em}{w}\hspace{.24cm}{\small\href{http://pordlabs.ucsd.edu/wryoung/}{http://pordlabs.ucsd.edu/wryoung/}}\end{minipage}\\
\mbox{}&\\
\begin{minipage}[c]{.55\textwidth}
\raggedright \textbf{Andy McC. Hogg} (postdoc supervisor)\\
Research School of Earth Sciences\\
Australian National University\\
Canberra, ACT 2601, Australia\\
{\fontspec{Meiryo}{☎}}\hspace{.188cm}\texttt{\href{skype:+61261259962?sms}{+61$\;$2$\;$61259962}}\\
\hspace{.1em}{\fontspec{Arial Unicode MS}{✉}}\hspace{-.1em}\hspace{.32cm}{\small\href{mailto:andy.hogg@anu.edu.au}{andy.hogg@anu.edu.au}}\\
\hspace{.1em}{w}\hspace{.24cm}{\small\href{http://rses.anu.edu.au/people/academics/prof-andy-hogg}{http://rses.anu.edu.au/people/academics/prof-andy-hogg}}\end{minipage}%
&
\begin{minipage}[c]{.48\textwidth}
\raggedright \textbf{Brian F. Farrell}\\
Department of Earth and Planetary Sciences\\
Harvard University\\
Cambridge, MA 02138, USA\\
{\fontspec{Meiryo}{☎}}\hspace{.188cm}\texttt{\href{skype:+16174952998?sms}{+1$\;$(617)$\;$495-2998}}\\
\hspace{.1em}{\fontspec{Arial Unicode MS}{✉}}\hspace{-.1em}\hspace{.32cm}{\small\href{mailto:farrell@seas.harvard.edu}{farrell@seas.harvard.edu}}\\
\hspace{.1em}{w}\hspace{.24cm}{\small\href{http://brian-f-farrell.fas.harvard.edu/}{http://brian-f-farrell.fas.harvard.edu}}\end{minipage}\\



% \begin{minipage}[c]{.48\textwidth}
% \raggedright \textbf{Javier Jim\'enez}\\
% School of Aeronautics\\
% Universidad Polit\'ecnica de Madrid\\
% Madrid, 28040, Spain\\
% {\fontspec{Meiryo}{☎}}\hspace{.188cm}\texttt{\href{skype:+34913366361?sms}{+34$\;$913366361}}\\
% \hspace{.1em}{\fontspec{Arial Unicode MS}{✉}}\hspace{-.1em}\hspace{.32cm}{\small\href{mailto:jimenez@torroja.dmt.upm.es}{jimenez@torroja.dmt.upm.es}}\\
% \mbox{}\end{minipage}\\



% \begin{minipage}[c]{.48\textwidth}
% \raggedright \textbf{Nikolaos A. Bakas}\\
% Department of Physics\\
% University of Ioannina\\
% Ioannina, 452\,21, Greece\\
% {\fontspec{Meiryo}{☎}}\hspace{.188cm}\texttt{\href{skype:+302651008599?sms}{\small +30$\;$26510$\;$08599}}\\
% \hspace{.1em}{\fontspec{Arial Unicode MS}{✉}}\hspace{-.1em}\hspace{.32cm}{\small\href{mailto:nbakas@uoi.gr}{nbakas@uoi.gr}}\\
% %\hspace{.1em}{w}\hspace{.24cm}{\small\href{http://users.uoa.gr/~thapostol/}{http://users.uoa.gr/$\sim$thapostol}} \\
% \mbox{}
% \end{minipage}%

%\begin{minipage}[c]{.48\textwidth}
%\raggedright \textbf{Theocharis A. Apostolatos}\\
%Department of Physics\\
%\ekpa\\
%Zografos, 157\,84, Greece\\
%{\fontspec{Meiryo}{☎}}\hspace{.188cm}\texttt{\href{skype:+302107276902?sms}{\small +30$\;$210$\;$7276902}}\\
%\hspace{.1em}{\fontspec{Arial Unicode MS}{✉}}\hspace{-.1em}\hspace{.32cm}{\small\href{mailto:thapostol@phys.uoa.gr}{thapostol@phys.uoa.gr}} \\
%\hspace{.1em}{w}\hspace{.24cm}{\small\href{http://users.uoa.gr/~thapostol/}{http://users.uoa.gr/$\sim$thapostol}} \\
%\mbox{}
%\end{minipage}%


\end{tabular}

\vfill{}
%\hrulefill


\begin{center}
{\scriptsize  Last updated: \today}
\end{center}

\end{document}
